---
title: "Simple document"
author: "Jessie Li"
date: "09-12-2023"
output: github_document
---

I'm an R Markdown document! 

# Section 1: First code chunk
Import library tidy verse:
```{r}
library(tidyverse)
```

# Section 2: Make a plot

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: Learning assessment!

This code is aborrowed from last lecture; it creates a dataframe for plotting
```{r}
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000)
  )
```

And this code creates a histogram of plot_df: 
```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

This code chunk should creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. 

Solution

```{r tibble_table}
tibble_table = 
  tibble(
    numeric_samp = rnorm(500, mean=1),
    logical_vec = numeric_samp > 0,
    absolute_val = abs(numeric_samp)
  )

ggplot(tibble_table, aes(x = absolute_val)) + geom_histogram()

median_samp = median(pull(tibble_table, numeric_samp))
```

The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.


# Section 4: Text formating examples

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell
